\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-10 paper/main.tex
.

Both approaches may be used in conjunction with network inference
\cite{}.

>>>>

Both approaches may be used in conjunction with network inference
\cite{}. Biological networks used for DTI prediction include
protein--protein interaction networks \cite{} and networks including
several other types of biological relations, including similarity
between represented entities \cite{PREDICT}. Network-based DTI
prediction methods use the guilt-by-association principle \cite{} and
assume that a protein is a likely target for a drug if many of the
protein's neighbors in the interaction network are targets of the
drug \cite{}.
